---
title       : ROC Plotting of Performance using "roll belt"" and "yaw belt"" features prediction
subtitle    : Gamma and Cost adjustable SVM model with ROC Analysis
author      : Ron Bjork
job         : Data Products Developer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: [libraries/nvd3]}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

### Support Vector Machines

This Data Product provides the user a way to 
explore the effects of gamma and cost parameters on 
the Support Vector Machine model for prediction. Below
is a classification plot of two gaussian distributed population differing 
in their mean. The red points belong to population 2. Gamma = 1  Cost = 1

```{r echo = F, results = 'asis'}
# require(rCharts)
# haireye = as.data.frame(HairEyeColor)
# n1 <- nPlot(Freq ~ Hair , group = 'Eye', type = 'multiBarChart',
#   data = subset(haireye, Sex == 'Male')
# )
# n1$print('chart1')


# Since the data below works perhaps 
# best strategy is to simply shape the data of interest, that above,
# into that below:
set.seed(1)
x=matrix(rnorm(200*2),ncol=2)
x[1:100,]=x[1:100,]+2
x[101:150,]=x[101:150,]-2
y=c(rep(1,150),rep(2,50))
dat=data.frame(x=x,y=as.factor(y))

train=sample(200,100)


modelFit <- svm(y~., data=dat[train,],kernel="radial",gamma=1,cost=1,decision.values=T)
modelFit2 <- svm(y~., data=dat[train,],kernel="radial",gamma=20,cost=1,decision.values=T)

plot(modelFit,dat[-train,],page=FALSE,new=TRUE)
```

---

Gamma = 20  Cost = 1   Notice the tighter region around Selected. This will reduce False positives but will also overfit the model some. But we can change the cost to improve the optimal SVM.

```{r echo = F, results = 'asis'}
p1 <- plot(modelFit2,dat[-train,],page=FALSE,new=TRUE)

```
<table><tr><td>`r p1 `</td></tr></table>

--- .class #id 

### Classification and Confusion Matrix

Using "Gamma = 1  Cost = 1", the confusion matrix is calculated with 
values for Accuracy, Sensivity, Specifity, False Positives and True positives calculated.


```{r echo = F, results = 'asis'}

fitted <- attributes(predict(modelFit, dat[train,], decision.values=TRUE))$decision.values
predictionsTest <- predict(modelFit,dat[-train,],decision.values=T)
fittedTest <- attributes(predictionsTest)$decision.values

cm <- confusionMatrix(predictionsTest,dat[-train,"y"])

fpr <- cm$table[3]/(cm$table[1] + cm$table[3])
tpr <- cm$table[4]/(cm$table[2] + cm$table[4])

```
<table>
<tr><td></td><td></td><td colspan=2><b>Truth</b></td></tr>
<tr><td></td><td></td><td>negative</td><td>positive</td></tr>
<tr><td><b>Prediction</b></td><td>negative</td><td>`r cm$table[1]`</td><td>`r cm$table[3]`</td></tr>
<tr><td></td><td>positive</td><td>`r cm$table[2]`</td><td>`r cm$table[4]`</td></tr>
</table>

<table>
<tr><td>Accuracy:`r cm$overall[1]`</td></tr>
<tr><td>False Positives Rate:$$\frac{`r cm$table[2]`}{`r cm$table[1]` + `r cm$table[2]`}$$ = `r fpr`</td></tr>
<tr><td>True Positives Rate: $$\frac{`r cm$table[4]`}{`r cm$table[3]` + `r cm$table[4]`}$$ = `r tpr`</td></tr>
</table>



---

### Its ROC

```{r echo = F, results = 'asis'}

rocplot <- function(pred,truth, ...){
  predob = prediction(pred,truth)
  perf = performance(predob,"tpr","fpr")
  plot(perf,...)
}

rocplot(fitted,dat[train,"y"],main="ROC - black:Train data, red:Test data")
rocplot(fittedTest,dat[-train,"y"],add=T,col="red")
```
